---
title: "Replication Unified Democracy"
author: "Ahmad Qabazard"
date: "4/18/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##PART I

##Load required packages
```{r include=FALSE}
library(devtools)
library(tidyverse)
library(haven)
library(dplyr)
```

##Take look at the data
```{r include=FALSE}
PA_DTA_file <- read_dta("/Users/ahmad/Documents/University of Iowa /Computational Methods/Replication-Homework/replication-homework/PA_DTA_file.dta")
#View(PA_DTA_file)
uds_1000 <- read.csv("/Users/ahmad/Documents/University of Iowa /Computational Methods/Replication-Homework/replication-homework/uds_1000.csv")
uds <- uds_1000 %>%
mutate(id=cowcode)

uds <- uds %>% 
arrange(id, year) %>% 
select(country, id, year, everything())

#mydata <- left_join(PA_DTA_file, uds, by=c("id","year"))
str(PA_DTA_file)
str(uds$id)
str(droplevels.data.frame(PA_DTA_file))
PA_DTA_file[] <- lapply(PA_DTA_file, function(x) {attributes(x) <- NULL; x})
mydata <- left_join(PA_DTA_file, uds, by=c("id", "year"))
```

## Drop variables not used (analysis 1976 - 1992) 
```{r include=FALSE}
dataset <- PA_DTA_file %>%
  filter(year > "1974")
dataset <- subset(dataset, dv1==1 & dv2==1 & dv3==1)
```

## Duplicates 

The state dofile drops duplicates to "corrects problem in the initial UDS release." However, I did not find any duplicates. I will skip this step and revisit if problems arise. 

##Panel corrected standard errors using pcse 
```{r include=FALSE}
#install.packages("pcse")
library(pcse)
pcse_table <- lm(polityiv ~ lag(pcaplog, 1) + lag(rgdppcgr, 1) + lag(open, 1) + lag(cpi, 1) + lag(prime, 1) + lag(second, 1) + lag(presiden, 1) + lag(parliamn, 1) + lag(bksfrac, 1), data = dataset)
pcse <- pcse(pcse_table, groupN = dataset$id, groupT = dataset$year, pairwise = TRUE)
```
The pairwise command should have dealt with the issue of unbalanced data? Also no duplicates in the data. 

```{r include=FALSE}
duplicated(dataset$uniqueid)
```

##Panel corrected standard errors using plm 
```{r include=FALSE}
#install.packages("plm")
library(plm)
dataset1 <- dataset %>% 
  mutate(l.pcaplog = lag(pcaplog, k=1),
l.rgdppcgr = lag(rgdppcgr, k=1),
l.open = lag(open, k=1),
l.cpi = lag(cpi, k=1),
l.prime = lag(prime, k=1),
l.second = lag(second, k=1),
l.presiden = lag(presiden, k=1),
l.parliamn= lag(parliamn, k=1),
l.bksfrac= lag(bksfrac, k=1))

mydata_panel <- pdata.frame(dataset1, index =c("id", "year"))
lm_model_panel <- plm(polityiv ~ l.pcaplog + l.rgdppcgr + l.open + l.cpi + l.prime + l.second + l.presiden + l.parliamn + l.bksfrac, data = mydata_panel, model = "pooling")
summary(lm_model_panel)
```

```{r include=FALSE}
mydata_panel <- pdata.frame(dataset, index =c("id", "year"))
lm_model_panel <- plm(polityiv ~ lag(pcaplog, 1) + lag(rgdppcgr, 1) + lag(open, 1) + lag(cpi, 1) + lag(prime, 1) + lag(second, 1) + lag(presiden, 1) + lag(parliamn, 1) + lag(bksfrac, 1), data = mydata_panel, model = "pooling")
summary(lm_model_panel)

```

##Declare data to be time series 
```{r}
ts(dataset1, start=c(1975), end=c(1992), frequency=1)
dataset1 <- dataset %>% 
  mutate(l.pcaplog = lag(pcaplog, k=1),
l.rgdppcgr = lag(rgdppcgr, k=1),
l.open = lag(open, k=1),
l.cpi = lag(cpi, k=1),
l.prime = lag(prime, k=1),
l.second = lag(second, k=1),
l.presiden = lag(presiden, k=1),
l.parliamn= lag(parliamn, k=1),
l.bksfrac= lag(bksfrac, k=1))

mydata_panel <- pdata.frame(dataset1, index =c("id", "year"))
lm_model_panel <- plm(polityiv ~ l.pcaplog + l.rgdppcgr + l.open + l.cpi + l.prime + l.second + l.presiden + l.parliamn + l.bksfrac, data = mydata_panel, model = "pooling")
summary(lm_model_panel)


pcse_table <- lm(polityiv ~ lag(pcaplog, 1) + lag(rgdppcgr, 1) + lag(open, 1) + lag(cpi, 1) + lag(prime, 1) + lag(second, 1) + lag(presiden, 1) + lag(parliamn, 1) + lag(bksfrac, 1), data = dataset1)
pcse <- pcse(pcse_table, groupN = dataset1$id, groupT = dataset1$year, pairwise = TRUE)

```


##Prais-Winsten. Different model, but an alternative that works.

```{r include=FALSE}
#install.packages("prais")
library(prais)
polity <- prais_winsten(polityiv ~ lag(pcaplog, 1) + lag(rgdppcgr, 1) + lag(open, 1) + lag(cpi, 1) + lag(prime, 1) + lag(second, 1) + lag(presiden, 1) + lag(parliamn, 1) + lag(bksfrac, 1), data = dataset)
summary(polity)

vanhanen <- prais_winsten(polityiv ~ lag(pcaplog, 1) + lag(rgdppcgr, 1) + lag(open, 1) + lag(cpi, 1) + lag(prime, 1) + lag(second, 1) + lag(presiden, 1) + lag(parliamn, 1) + lag(bksfrac, 1), data = dataset)
summary(vanhanen)

freedom <- prais_winsten(polityiv ~ lag(pcaplog, 1) + lag(rgdppcgr, 1) + lag(open, 1) + lag(cpi, 1) + lag(prime, 1) + lag(second, 1) + lag(presiden, 1) + lag(parliamn, 1) + lag(bksfrac, 1), data = dataset)
summary(freedom)
```

```{r include=FALSE }
library("stargazer")
stargazer(polity, vanhanen, freedom, 
          type = "latex",
          title="Casper and Tufis (2003) Table 1, Columns 5, 6, and 7.",
align=TRUE, dep.var.labels=c("Polity", "Vanhanen", "Freedom House"),
covariate.labels=c("GDP pc, logged","Real GDP pc growth",
"Openness","Inflation","Primary Education","Secondary Education", "Presidential", "Parliamentary", "Party Fractionalization", "Constant"),
omit.stat=c("LL","ser"), ci=TRUE)
```


##PART II 
```{r include=FALSE }
require(foreign)
require(sandwich)
require(lmtest)
require(MASS)
require(Hmisc)
require(stargazer)
require(sciplot)
require(lme4)
```

```{r}
dataset <- mydata %>%
  filter(year > "1974")
```



```{r include=FALSE }
# Load function to incorporate uncertainty (with robust standard errors)
milm <- function(fml, midata){
  xx <- terms(as.formula(fml))
  lms <- matrix(data=NA, nrow=(length(attr(xx, "term.labels")) + 1), ncol=length(midata))
  ses <- matrix(data=NA, nrow=(length(attr(xx, "term.labels")) + 1), ncol=length(midata))
  vcovs <- list()
  for(i in 1:length(midata)){
    tmp <- lm(formula=as.formula(fml), data=midata[[i]])
    lms[,i] <- tmp$coefficients
    ses[,i] <- sqrt(diag(vcovHC(tmp, type = "HC")))
    vcovs[[i]] <- vcovHC(tmp, type = "HC")
  }
  par.est <- apply(lms, 1, mean)
  se.within <- apply(ses, 1, mean)
  se.between <- apply(lms, 1, var)
  se.est <- sqrt(se.within^2 + se.between*(1 + (1/length(midata))))
  list("terms"=names(tmp$coefficients), "beta" = par.est, "SE"=se.est, "vcovs"=vcovs,"coefs" = lms)   
}
```

##We need the dependent variable: mean of UDS' posterior densities  
